### 2013-09-26 exact_learning/paper.tex
more fixes via vlad :)

In this chapter, we investigate the necessity and consequences of these
approximations in the $1$-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and \textsc{Pascal VOC} datasets. Our
approach improves upon the state-of-the-art on the MSRC-21 dataset, and is
competative with comparable approaches on the \textsc{Pascal VOC} dataset.% and nyu?

@@

While empirically exact learning yields results comparable to those using
approximate inference alone, certification of optimality allows treating
learning as a black-box, enabling the researcher to focus attention on
designing the model for the application at hand.

@@

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, inference oracle $\hat{I}$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{align*}
                (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:\\
            &\theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi
            \end{align*}
            \For {i=1, \dots, k}
                \State
            $\hat{y}\hoch{i} \leftarrow \hat{I}(x\hoch{i}, y\hoch{i}, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
        \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the $1$-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. Recall the optimization problem
that is solved by the $1$-slack cutting plane algorithm:
\begin{align*}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi \numberthis\label{eq:oneslack_again}\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align*}
For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack} is reproduced as
Algorithm~\ref{alg_one_slack_again}, with the additional input of an inference algorithm $\hat{I}$, which is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $\hat{I}$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified in
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $\hat{I}(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $\hat{I}(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?

@@

Let $o_{\W}(\theta)$ denote objective \Eqref{oneslack_again} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{line_restricted} of Algorithm~\ref{alg_one_slack_again} and  let
\[
    o^{\hat{I}}(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $\hat{I}$, that is $o^{\hat{I}}(\theta)$ is the approximation of the primal
objective given by $\hat{I}$. To simplify exposure, we drop the dependency on $\theta$.

@@

As a fast under-generating inference algorithm, we used fusion
moves~\citep{rother2007optimizing, lempitsky2010fusion}. Fusion moves are a local
search procedure, using moves that are generated using an auxiliar binary problem,
which is solved using QPBO~\cite{rother2007optimizing}.

@@

\Figref{caching} shows a visual comparison that highlights the differences
between the methods. Note that neither $o^Q$ nor $o^C$ provide valid upper bounds on the objective,
which is particularly visible for $o^C$ using the method of \cite{joachims2009cutting}.
Using no cache leads to a relatively smooth, but slow convergence, as inference is run often.
Using the method of \citet{joachims2009cutting}, each run of the separation oracle is followed by
quick progress of the dual objective $o_\W$, which flattens out quickly. Much time is then spent adding
constraints that do not improve the dual solution.
Our heuristic instead probes the cache, and only proceeds using cached constraints if the resulting
$o^C$ is not to far from $o^Q$.

@@

\subsubsection{Pascal VOC 2010}
For the \textsc{Pascal} VOC 2010 dataset, we follow the procedure from \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \cite{xia2012segmentation}, who 
evaluate on the \textsc{Pascal} VOC 2010 ``test'' set.

>>>>

In this chapter, we investigate the necessity and consequences of these
approximations in the $1$-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and \textsc{Pascal VOC} datasets. Our
approach improves upon the state-of-the-art on the MSRC-21 dataset, and is
competative with comparable approaches on the \textsc{Pascal VOC} dataset.

@@

While empirically exact learning yields results comparable to those using
approximate inference alone, certification of optimality allows treating
learning as a black-box, enabling the researcher to focus attention on
designing the model for the application at hand. It also makes research more
reproducible, as the particular optimization methods that are used become less
relevant to the result.

@@

\begin{algorithm*}[t]
    \caption{1-Slack Cutting Plane Training of Structural SVMs \label{alg_one_slack_again}}
    \begin{algorithmic}[1]
        \Require training samples $\{ (x\hoch{i}, y\hoch{i}), \dots, (x\hoch{i}, y\hoch{i})\}$, regularization parameter $C$, stopping tolerance $\epsilon$, inference oracle $\hat{I}$.
        \Ensure parameters $\theta$, slack $\xi$
        \State $\W \leftarrow \emptyset$
        \Repeat
            \State \label{line_restricted}
            \vspace{-5mm}
            \begin{flalign*}
            \quad\quad    (\theta, \xi) \leftarrow \displaystyle &\argmin_{\theta, \xi} \frac{||\theta||}{2}^2 + C \xi&\\
            &\text{s.t. }\forall \hat{\mathbf{y}}=(\hat{y}\hoch{1}, \dots, \hat{y}\hoch{k}) \in \W:&\\
            &\theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] \geq \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \xi&
            \end{flalign*}
            \For {i=1, \dots, k}
                \State
            $\hat{y}\hoch{i} \leftarrow \hat{I}(x\hoch{i}, y\hoch{i}, \theta) \approx \displaystyle \argmax_{\hat{y}\in\mathcal{Y}} \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y})]$ \label{get_cutting_plane_again}
            \EndFor
            \State $\W \leftarrow \W \cup \{ (\hat{y}\hoch{i}, \dots, \hat{y}\hoch{i}) \} $
        \State $ \displaystyle \xi' \leftarrow  \sum_{i=1}^k \delta(y\hoch{i}, \hat{y}\hoch{i}) - \theta^T \sum_{i=1}^k [\Phi(x\hoch{i}, y\hoch{i}) - \Phi(x\hoch{i}, \hat{y}\hoch{i})] $
        \Until $\xi' - \xi < \epsilon$ \label{convergence_check}
    \end{algorithmic}
\end{algorithm*}

\section{Learning SSVMs with Approximate Inference}
In this chapter, we use the $1$-slack cutting plane algorithm, as we found this
algorithm to be most suitable for out approach. Recall the optimization problem
that is solved by the $1$-slack cutting plane algorithm:
\begin{align*}
    \min_{\theta, \xi}\ &\frac{1}{2} ||\theta||^2 + C \xi \numberthis\label{eq:oneslack_again}\\
    \text{s.t. }&\forall \hat{\mathbf{y}}=(\hat{y}^1, \dots, \hat{y}^n) \in \mathcal{Y}^n:\\
        &\theta^T \sum_{i=1}^n [\Phi(x^i, y^i) - \Phi(x^i,
            \hat{y}^i)] \geq \sum_{i=1}^n \Delta(y^i, \hat{y}^i)
            - \xi
\end{align*}
For reference, the algorithm described in
\Secref{one_slack}, Algorithm~\ref{alg_one_slack} is reproduced as
Algorithm~\ref{alg_one_slack_again}, with the additional input of an inference algorithm $\hat{I}$, which is called in
line~\ref{get_cutting_plane_again}. We investigate algorithms $\hat{I}$ (often called
separation
oracles in the context) that do not yield the exact maximum here.
There are two groups of inference procedures, as identified by
\citet{finley2008training}: under-generating and over-generating approaches.
An under-generating approach satisfies $\hat{I}(x^i, y^i, \theta) \in
\mathcal{Y}$, but does not guarantee maximality in line~\ref{get_cutting_plane_again}
of Algorithm~\ref{alg_one_slack_again}. An over-generating approach on the other
hand, does solve the loss-augmented prediction in line~\ref{get_cutting_plane_again}
exactly, but for a larger set $\hat{\mathcal{Y}} \supset \mathcal{Y}$, meaning
that possibly $\hat{I}(x^i, y^i, \theta) \notin \mathcal{Y}$.
%We elaborate on
%the properties of under-generating and over-generating inference procedures in
%Section~\ref{bounds}. %TODO Filler sentence? wat?

@@

Let $o_{\W}(\theta)$ denote the objective in \Eqref{oneslack_again} with
given parameters $\theta$ restricted to a working set $\W$, as computed in
line~\ref{line_restricted} of Algorithm~\ref{alg_one_slack_again} and  let
\[
    o^{\hat{I}}(\theta) = C\xi' + \frac{||\theta||}{2}^2
\]
when using inference algorithm $\hat{I}$, that is $o^{\hat{I}}(\theta)$ is the approximation of the primal
objective given by $\hat{I}$. To simplify exposure, we drop the dependency on $\theta$.

@@

As a fast under-generating inference algorithm, we used fusion
moves~\citep{rother2007optimizing, lempitsky2010fusion}. Fusion moves are a local
search procedure, using moves that are generated using an auxiliar binary problem,
which is solved using QPBO~\citep{rother2007optimizing}.

@@

\Figref{caching} shows a visual comparison that highlights the differences
between the methods. Note that neither $o^Q$ nor $o^C$ provide valid upper bounds on the objective,
which is particularly visible for $o^C$ using the method of \citet{joachims2009cutting}.
Using no cache leads to a relatively smooth, but slow convergence, as inference is run often.
Using the method of \citet{joachims2009cutting}, each run of the separation oracle is followed by
quick progress of the dual objective $o_\W$, which flattens out quickly. Much time is then spent adding
constraints that do not improve the dual solution.
Our heuristic instead probes the cache, and only proceeds using cached constraints if the resulting
$o^C$ is not too far from $o^Q$.

@@

\subsubsection{Pascal VOC 2010}
For the \textsc{Pascal} VOC 2010 dataset, we follow the procedure from \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \citet{xia2012segmentation}, who 
evaluate on the \textsc{Pascal} VOC 2010 ``test'' set.

### 2013-09-26 nyu/paper.tex
more fixes via vlad :)

\citet{stueckler2013} extended the approach of \citet{stuckler2012semantic} to
a real-time system for online learning and prediction of semantic classes.
Their method use a GPU implementation of random forests, and integrate 3D scene
information in an online fashion. They evaluated their approach on the dataset
of \citet{SilbermanECCV12} with promising results.  We use the implementation
of random forest provided by \citet{stueckler2013}, but instead of integrating
predictions over time, we focus on exploiting the structure within a single
frame.

@@

Our approach is implemented using our \textsc{PyStruct}
library introduced in \Secref{pystruct}.
%
All hyper parameters were adjusted using 5-fold cross-validation. The
hyper parameters of the random forests were found using the \textsc{hyperopt}
framework of \cite{bergstra2011algorithms}. For the CRF model, the only
hyper-parameters are related to the superpixel segmentation, and the single
hyper-parameter $C$ of the structural SVM formulation. These were adjusted
using grid-search.
We found 500 superpixels per image to work best, which allow for a maximum
possible performance of 95\% average class accuracy on the validation set.

@@

We did not explicitly address real time application, the random
forest implementation that we build upon allows for real-time
processing~\citep{stueckler2013}. The SLIC superpixel algorithm can also be
implemented on GPU in real-time, as was demonstrated by \citep{ren2011gslic}, and similarly
the normal features we use also have
real-time capabilities~\citep{holz_2011_robocup}.
Finally, fusion move inference for our model is very efficient for our model,
opening up the possibility to implement our approach entirely in real time.

>>>>

\citet{stueckler2013} extended the approach of \citet{stuckler2012semantic} to
a real-time system for online learning and prediction of semantic classes.
Their method use a GPU implementation of random forests, and integrate 3D scene
information in an online fashion. They evaluated their approach on the dataset
of \citet{SilbermanECCV12} with promising results.  We use the implementation
of random forests provided by \citet{stueckler2013}, but instead of integrating
predictions over time, we focus on exploiting the structure within a single
frame.

@@

Our approach is implemented using our \textsc{PyStruct}
library introduced in \Secref{pystruct}.
%
All hyper parameters were adjusted using 5-fold cross-validation. The
hyper parameters of the random forests were found using the \textsc{hyperopt}
framework of \citet{bergstra2011algorithms}. For the CRF model, the only
hyper-parameters are related to the superpixel segmentation, and the single
hyper-parameter $C$ of the structural SVM formulation. These were adjusted
using grid-search.
We found 500 superpixels per image to work best, which allow for a maximum
possible performance of 95\% average class accuracy on the validation set.

@@

We did not explicitly address real time application; the random
forest implementation that we build upon allows for real-time
processing~\citep{stueckler2013}. The SLIC superpixel algorithm can also be
implemented on GPU in real-time, as was demonstrated by \citep{ren2011gslic}, and similarly
the normal features we use also have
real-time capabilities~\citep{holz_2011_robocup}.
Finally, fusion move inference for our model is very efficient for our model,
opening up the possibility to implement our approach entirely in real time.
